Synpotic Soil Characterization

### 2022-12-21 3-reports/characterization_report.Rmd
ferrozine graphs
mehlich-extractable P
icr graphs

>>>>

**HCl-extractable iron - ferrozine method**

Extracted using 0.5 M HCl

```{r iron-ferrozine, fig.height=5, fig.width=7}
tar_read(gg_ferrozine)
```

**Mehlich-3 extractable P**

Extracted using Mehlich-3 solution, analyzed with molybdate method

```{r phosphorus-mehlich, fig.height=5, fig.width=7}
tar_read(gg_mehlich)
```

**FT-ICR-MS**

```{r, icr-vk}
tar_read(gg_icr_vankrevelen)
```

```{r, icr-unique}
tar_read(gg_icr_unique)
```

```{r, icr-pca}
tar_read(gg_icr_pca)
```
